Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
endring under data description
Images.
flyttet bilde
Adding images.

@@

<!--# Parenthesis as footnote? -->

@@

#### Key Performance Indicators

@@

### Details tab

@@

>>>>

<!-- Insert images here -->

@@

@@

```{r, out.width="50%", fig.cap="The main dashboard page", fig.align='center', echo=FALSE}
knitr::include_graphics("Images/Dashboard_page_1.png")
```
#### Key Performance Indicators

@@

### Details tab
```{r dashboard_page_2, out.width="50%", fig.cap="The details tab of the dashboard.", echo=FALSE}
knitr::include_graphics("Images/Dashboard_page_2.png")
```

@@

```{r dashboard_report_image, echo=FALSE, out.width="50%"}
knitr::include_graphics("Images/Dashboard_report.png")
```
